### 2020-04-22 final_report/tbr_final_report-metadata.tex
Remake abstract

% Abstract - % directly after { is important for correct indentation
\DISAbstract{%
  Surrogate modelling techniques have been employed in diverse areas of research to resolve the limitations of resource-expensive procedure with significantly cheaper approximations. In this internship project, we sought to develop a fast and high-quality surrogate model for simulations of the tritium breeding ratio (TBR) for under-design Tokamak nuclear fusion reactors. We investigated possibilities for dimensional reduction on the parameter space of a Monte Carlo TBR model in use at the UK Atomic Energy Authority. We investigated possibilities for dimensional reduction on the parameter space of this model, and reviewed $N$ classes of surrogate models for potential applicability. Here we present the performance and scaling properties of these surrogate models, the best of which demonstrated an accuracy of $X$ and a mean prediction time of $X$, representing a relative speedup $X$ with respect to the MC model. We further present a novel adaptive sampling algorithm, QASS, capable of interfacing with any of the individual studied models. Our preliminary testing on a toy TBR theory has demonstrated the efficacy of this algorithm for speeding up the surrogate modelling process.
}

>>>>

% Abstract - % directly after { is important for correct indentation
\DISAbstract{%
 The tritium breeding ratio (TBR) is an essential quantity for the design of modern and next-generation Tokamak nuclear fusion reactors. Representing the ratio between tritium fuel generated in breeding blankets at the boundary of the reactor, and fuel consumed during reactor runtime, the TBR depends in a complex manner on reactor geometry and material properties. We explored the training of surrogate models to produce a cheap but high-quality approximations for a Monte Carlo TBR model in use at the UK Atomic Energy Authority. We investigated possibilities for dimensional reduction on the parameter space of this model, and reviewed $N$ classes of surrogate models for potential applicability. Here we present the performance and scaling properties of these surrogate models, the best of which demonstrated an accuracy of $X$ and a mean prediction time of $X$, representing a relative speedup $X$ with respect to the MC model. We further present a novel adaptive sampling algorithm, QASS, capable of interfacing with any of the individual studied models. Our preliminary testing on a toy TBR theory has demonstrated the efficacy of this algorithm for speeding up the surrogate modelling process.
}
